---
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 3
---




<!-- Javascript for zooming on figures (adapted from: https://stackoverflow.com/questions/40401680) -->

<!-- Jquery import conflicts with DT::datatable so needs to be commented here -->
<!-- <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script> -->

<style>
.zoomDiv {
  display: none;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  background-color: #FFFFFF;
  box-shadow: 0px 0px 50px #888888;
  width: fit-content;
  max-width: 90%;
  max-height: 90%;
  overflow: auto;
}

.zoomImg {
  width: 100%;
}
</style>

<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick for all img except the zoomed one and link ones (filter)
    // use 'img.zoom' and out.extra='class=\"zoom\"' in chunk to specify manually which chunk images can be zoomed
    $('img:not(.zoomImg)').filter(':not(a *)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').show();
    });
    // onClick function for hiding div
    $('img.zoomImg').click(function() {
      $('.zoomDiv').hide();
    });
  });
</script>




```{r rmd_setKnitrOptions, include=FALSE}
# Set hook for PNG optimization ('optipng' must be installed on system)
#knitr::knit_hooks$set(optipng = knitr::hook_optipng)

# Set chunks default options
knitr::opts_chunk$set(results='asis',
                      echo = FALSE,           # Do not show chunks code
                      message = FALSE,        # Hide R regular text output in reports
                      warning = FALSE,         # Show warning messages
                      error = FALSE,          # Stop generating report on errors
                      cache = FALSE,          # Disable chunk result caching
                      cache.comments = FALSE, # Changing comments does not invalidate cache
                      fig.dim = c(5, 5),      # Size of device for R figures
                      autodep = TRUE,         # Automatic chunk dependencies if cache enabled
                      optipng = '-o2');       # PNG optimization level (2=default, 5=slow, 7=very slow)

# Set RMarkdown compatible format for kable 
options(knitr.table.format = 'markdown')
```




<!-- Load spectrum color picker code -->
```{js loadSpectrumJS, echo = FALSE, code=readLines("spectrum.js")}
```
```{css loadSpectrumCSS, echo = FALSE, code=readLines("spectrum.css")}
```

<!-- Prepare a js function extracting traces color from plotly figure -->
```{js getColorTab, echo = FALSE}

// Ask figure template from plotly, extract markers color (scatter and scattergl only), and place them in clipboard
getColorTab = function(plotLyFigure, type = "scatter", colorFormatFun = "hex") 
  { 
    var template = Plotly.makeTemplate(plotLyFigure);
    var resultColorString = "";
    for (curTrace in template.data[type])
    {
      // Only use traces having markers
      if(template.data[type][curTrace].mode == "markers") resultColorString += '"' + template.data[type][curTrace].name + '" = "' + tinycolor(template.data[type][curTrace].marker.color).toString(colorFormatFun) + '"\n';
    }
    // Create a dummy element to copy content to clipboard
    var textarea = document.createElement("textarea"); textarea.textContent = resultColorString; textarea.style.position = "fixed"; document.body.appendChild(textarea); textarea.select(); document.execCommand("copy"); document.body.removeChild(textarea);
    alert("\n" + resultColorString + "\n\nCopied to clipboard !");
  } 
```




```{r rmd_loadParamsAndDependencies, warning=FALSE, cache = FALSE}
### Define working folder
WORKING_DIR   = getwd();


### Load libraries, global functions/variables, and chunks
source( file.path( WORKING_DIR, "00_generalDeps.R"));

# Import chunks from source files
read_chunk( path=file.path( WORKING_DIR, "01_prepareData.R"));
read_chunk( path=file.path( WORKING_DIR, "02_variableGenes.R"));
read_chunk( path=file.path( WORKING_DIR, "03_cellHeterogeneity_PCA.R"));
read_chunk( path=file.path( WORKING_DIR, "04_cellHeterogeneity_tSNE_UMAP.R"));
read_chunk( path=file.path( WORKING_DIR, "05_cellHeterogeneity_Clustering.R"));
read_chunk( path=file.path( WORKING_DIR, "06_plots_tables_dimreduc_clustering.R"));
read_chunk( path=file.path( WORKING_DIR, "07_cellHeterogeneity_MarkerGenes.R"));
#read_chunk( path=file.path( WORKING_DIR, "08_clusterFunctionalAnalysis.R"));
read_chunk( path=file.path( WORKING_DIR, "09_monitoredGenesAnalysis.R"));
read_chunk( path=file.path( WORKING_DIR, "10_modulesAnalysis.R"));
read_chunk( path=file.path( WORKING_DIR, "11_scatterGenes.R"));
read_chunk( path=file.path( WORKING_DIR, "90_finalize.R"));
```




---
title: `r paste( GLOBAL_DESCRIPTION, SAMPLE_NAME, ANALYSIS_STEP_NAME, sep ="<BR>")`
---




```{r rmd_initFunctions}

# Create output folders
<<createOutputFolders>>

### Record starting time (for report and file names)
startTime = Sys.time();
startTimeReport   = format( startTime, "%Y %m %d %H:%M:%S")
startTimeFileName = format( startTime, "%Y_%m_%d_%H_%M_%S")


### Initialize utils

# Create a hash for all parameters
paramsHash = digest( environment(), algo="crc32");

# Set seed for pseudo random number generator
set.seed(SEED);

# Set the use of multiple cores using 'future' library, as implemented in Seurat3 when possible
# https://github.com/satijalab/seurat/issues/457
plan(strategy = "multicore", workers = NBCORES);

```




# Run informations {.tabset .tabset-fade}

## Run
<center>
```{r rmd_runInfo_run}
pander( c( 'Date'     = startTimeReport,
           'Sample'   = EXPERIMENT_NAME,
           'Hash'     = paramsHash));
```
</center>

## Parameters
```{r rmd_runInfo_params}
listParams = as.list( paramsEnv);
pander(listParams[order(names(listParams))]); # Show params in alphabetical order
```

## System
<center>
```{r rmd_runInfo_sysInfo}
showSimpleDT( Sys.info())
```
</center>

## R
```{r rmd_runInfo_r}
pander( sessionInfo());
```

<!-- Ending the tabset section -->
<!-- ## {.toc-ignore} -->
<br /><br />


# Load Data

```{r rmd_dataLoad, warning = TRUE, fig.dim = c(9,6)}
<<loadData>>
<<normalizeData>>
```



<br /><br />




# Variable genes
```{r rmd_findVariableGenes}
<<findVariableGenes_seuratMethod>>
```

Number of variable genes found: `r variablesGenesStats`

```{r rmd_findVariableGenes_summaryPlot}
<<findVariableGenes_summaryPlot>>
```

<br />

Top `r VARIABLE_FEATURES_SHOWTOP` most variable annotations:

```{r rmd_findVariableGenes_summaryTable}
<<findVariableGenes_summaryTable>>
```
<br /><br />





# PCA results

PCA projections for dimensions `r paste( 1:PCA_PLOTS_NBDIMS, collapse="/")` (colored by batch)  
```{r rmd_heterogeneity_pca, out.width='33%'}
<<heterogeneity_pca>>
```
<br />

UMIs counts on PCA dimensions `r paste( 1:PCA_PLOTS_NBDIMS, collapse="/")`  
```{r rmd_heterogeneity_pca_umisCounts, out.width='33%'}
<<heterogeneity_pca_umisCounts>>
```
<br />

Genes counts on PCA dimensions `r paste( 1:PCA_PLOTS_NBDIMS, collapse="/")`  
```{r rmd_heterogeneity_pca_genesCounts, out.width='33%'}
<<heterogeneity_pca_genesCounts>>
```
<br />

Correlation (Spearman) of PCA dimensions `r paste( 1:PCA_PLOTS_NBDIMS, collapse="/")` with UMIs and genes counts  
```{r rmd_heterogeneity_pca_correlations, fig.dim = c(9,6)}
<<heterogeneity_pca_correlations>>
```
<br />

PCA loadings of top `r PCA_PLOTS_NBFEATURES` features for dimensions `r paste( 1:PCA_PLOTS_NBDIMS, collapse="/")`  
```{r rmd_heterogeneity_pca_loadings, fig.dim = c(4, 4), out.width='33%'}
<<heterogeneity_pca_loadings>>
```
<br /><br />




# Clustering & Dimensionality reduction
```{r rmd_dimreduc_clustering, warning=FALSE}
<<heterogeneity_dimReduc>>
<<heterogeneity_identifyClusters>>
<<plotsPreparation>>
```

## Cells counts
```{r rmd_dimreduc_clustering_counts, warning=FALSE}
<<plotClustersSize>>
<<plotClustersSizeByHTO>>
```

## QC statistics by cluster
```{r rmd_dimreduc_clustering_stats, warning=FALSE}
<<identifyClusters_splitStats>>
```




## Dimensionality reduction {.tabset .tabset-fade}

### Clusters {.tabset .tabset-fade .tabset-pills}
#### Interactive
```{r rmd_plotDimReducInteractive_colorClusters}
dimReducWidth  = 950;
dimReducHeight = 800;
initialPointSize = 5;
showDimReducClusterLabels = FALSE;
showLegend = TRUE;
<<plotDimReducInteractive_colorClusters>>
rm(showDimReducClusterLabels);
rm(showLegend);
```
<br />

#### Raster
```{r rmd_plotDimReducRaster_colorClusters}
showDimReducClusterLabels = TRUE;
showLegend = FALSE;
<<plotDimReducRaster_colorClusters>>
rm(showDimReducClusterLabels);
rm(showLegend);
```
<br />  

### Clusters + HTOs {.tabset .tabset-fade .tabset-pills}
#### Interactive
```{r rmd_plotDimReducInteractive_colorClusters_symbolHTOs}
dimReducWidth  = 950;
dimReducHeight = 800;
initialPointSize = 5;
showDimReducClusterLabels = FALSE;
showLegend = TRUE;
<<plotDimReducInteractive_colorClusters_symbolHTOs>>
rm(showDimReducClusterLabels);
rm(showLegend);
```
<br />  

#### Raster
```{r rmd_plotDimReducRaster_colorClusters_symbolHTOs, fig.dim = c(11, 9)}
showDimReducClusterLabels = FALSE;
showLegend = TRUE;
<<plotDimReducRaster_colorClusters_symbolHTOs>>
rm(showDimReducClusterLabels);
rm(showLegend);
```
<br />  

### Facet HTOs {.tabset .tabset-fade .tabset-pills}
<!-- #### Interactive -->
<!-- ```{r rmd_plotDimReducInteractiveGG_colorClusters_facetHTOs, warning = FALSE} -->
<!-- dimReducWidth  = 950; -->
<!-- dimReducHeight = 800; -->
<!-- initialPointSize = 5; -->
<!-- showDimReducClusterLabels = FALSE; -->
<!-- showLegend = TRUE; -->
<!-- <<plotDimReducInteractiveGG_colorClusters_facetHTOs>> -->
<!-- rm(showDimReducClusterLabels); -->
<!-- rm(showLegend); -->
<!-- ``` -->
<!-- <br />   -->

<!-- #### Raster -->
```{r rmd_plotDimReducRaster_colorClusters_facetHTOs, fig.dim = c(11, 9)}
showDimReducClusterLabels = FALSE;
showLegend = TRUE;
<<plotDimReducRaster_colorClusters_facetHTOs>>
rm(showDimReducClusterLabels);
rm(showLegend);
```
<br />  

### Facet Clusters {.tabset .tabset-fade .tabset-pills}
<!-- #### Interactive -->
<!-- ```{r rmd_plotDimReducInteractiveGG_colorHTOs_facetClusters, warning = FALSE} -->
<!-- dimReducWidth  = 950; -->
<!-- dimReducHeight = 800; -->
<!-- initialPointSize = 5; -->
<!-- showDimReducClusterLabels = FALSE; -->
<!-- showLegend = TRUE; -->
<!-- <<plotDimReducInteractiveGG_colorHTOs_facetClusters>> -->
<!-- rm(showDimReducClusterLabels); -->
<!-- rm(showLegend); -->
<!-- ``` -->
<!-- <br />   -->

<!-- #### Raster -->
```{r rmd_plotDimReducRaster_colorHTOs_facetClusters_allInBackground, fig.dim = c(11, 9)}
showDimReducClusterLabels = FALSE;
showLegend = TRUE;
<<plotDimReducRaster_colorHTOs_facetClusters_allInBackground>>
rm(showDimReducClusterLabels);
rm(showLegend);
```
<br />  




### Density: ref groups
```{r rmd_plotDimReducRaster_colorDensity_circleDensity_globalRefGroups, warning=FALSE, fig.dim = c(11, 9)}
<<plotDimReducRaster_colorDensity_circleDensity_prepareData>>

<<plotDimReducRaster_colorDensity_circleDensity_globalRefGroups>>
```
<br />  

### Density: Facet HTOs
```{r rmd_plotDimReducRaster_colorDensity_circleDensity_facetByHTO, warning=FALSE, fig.dim = c(9, 9)}
<<plotDimReducRaster_colorDensity_circleDensity_facetByHTO>>
```
<br />  

### Density: Facet Clusters + HTOs
```{r rmd_plotDimReducRaster_colorDensity_circleDensity_facetByHTOAndCluster, warning=FALSE, fig.dim = c(0.5+(2.5*length(table(cellsData[["Cluster"]]))), 0.5+(2.25*length(HTO_FACTOR_LEVELS)))}
<<plotDimReducRaster_colorDensity_circleDensity_facetByHTOAndCluster>>
```
<br />  

### Density: Facet Clusters + HTOs grouped
```{r rmd_plotDimReducRaster_colorDensity_circleDensity_facetByHTOGroupedAndCluster, warning=FALSE, fig.dim = c(0.5+(2.7*length(table(cellsData[["Cluster"]]))), 5)}
<<plotDimReducRaster_colorDensity_circleDensity_facetByHTOGroupedAndCluster>>
```
<br />  




# {.toc-ignore}
<br /><br />







# Marker genes
```{r rmd_heterogeneity_markerGenes}
<<heterogeneity_markerGenes>>
```

## Marker genes list
```{r rmd_heterogeneity_markerGenes_table}
<<heterogeneity_markerGenes_table>>
```
<br />

## Marker genes expression {.tabset .tabset-fade}

### UMAP {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_expression_projection_UMAP, fig.dim = c(4, 4), out.width='25%'}

cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_markerGenes_expression_projection>>

```

<!-- Ending the tabset section -->
<!-- ### {.toc-ignore} -->

<!-- ### tSNE {.tabset .tabset-fade} -->
<!-- ```{r rmd_heterogeneity_markerGenes_expression_projection_tSNE, fig.dim = c(4, 4), out.width='25%'} -->

<!-- cat("\n<a href='#clusters-projection'>"); -->
<!-- <<plotDimReducRaster_thumbnail>> -->
<!-- cat("</a> \n \n"); -->

<!-- <<heterogeneity_markerGenes_expression_projection>> -->

<!-- ``` -->

<!-- <!-- Ending the tabset section --> -->
<!-- #### {.toc-ignore} -->

### Clusters violin {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_expression_violin, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_markerGenes_expression_violin>>
```


### Clusters functional enrichment {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_functional_enrichment, fig.dim = c(9, 9) }
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

cat("Disabled in Rmd")
#<<heterogeneity_markerGenes_functional_enrichment>>
```


<br /><br />





# Monitored genes
```{r rmd_heterogeneity_monitoredGenes, warning = TRUE}
<<heterogeneity_monitoredGenes>>
```

## Monitored genes heatmap

Expression heatmap of monitored genes sorted by Seurat clusters:

```{r rmd_heterogeneity_monitoredGenes_heatmap, fig.dim = c(8, min(1+(length(unlist(MONITORED_GENES))/10), 150))}
#<<heterogeneity_monitoredGenes_heatmap>>
```

## Monitored genes expression {.tabset .tabset-fade}

### UMAP {.tabset .tabset-fade}
```{r rmd_heterogeneity_monitoredGenes_expression_projection_UMAP, fig.dim = c(4, 4), out.width='25%'}

cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_monitoredGenes_expression_projection>>

```

<!-- Ending the tabset section -->
<!-- #### {.toc-ignore} -->

<!-- #### tSNE {.tabset .tabset-fade} -->
<!-- ```{r rmd_heterogeneity_monitoredGenes_expression_projection_tSNE, fig.dim = c(4, 4), out.width='25%'} -->

<!-- cat("\n<a href='#clusters-projection'>"); -->
<!-- #<<plotDimReducRaster_thumbnail>> -->
<!-- cat("</a> \n \n"); -->

<!-- #<<heterogeneity_monitoredGenes_expression_projection>> -->

<!-- ``` -->

<!-- <!-- Ending the tabset section --> -->
<!-- #### {.toc-ignore} -->

### Clusters violin {.tabset .tabset-fade}
```{r rmd_heterogeneity_monitoredGenes_expression_violin, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_monitoredGenes_expression_violin>>
```

<!-- Ending the tabset section -->
<!-- #### {.toc-ignore} -->

<!-- Ending the tabset section -->
<!-- ### {.toc-ignore} -->
<br /><br />




# Modules analysis
```{r rmd_heterogeneity_modules}
<<heterogeneity_modules>>
<<heterogeneity_modules_scoring>>
```

## Modules scoring heatmap

Heatmap of modules scoring sorted by Seurat clusters:

```{r rmd_heterogeneity_modules_heatmap, fig.dim = c(8, min(1+(length(MODULES_GENES)/10), 150))}
<<heterogeneity_modules_heatmap>>
```

## Modules scoring {.tabset .tabset-fade}

### UMAP {.tabset .tabset-fade .tabset-pills}
```{r rmd_heterogeneity_modules_expression_projection_UMAP, fig.dim = c(4, 4), out.width='25%'}

cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_modules_expression_projection>>
#<<heterogeneity_modules_expression_projection_pngFile>>

```

<!-- Ending the tabset section -->
### {.toc-ignore}

### Clusters violin {.tabset .tabset-fade}
```{r rmd_heterogeneity_modules_expression_violin, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_modules_expression_violin>>
#<<heterogeneity_modules_expression_violin_pngFile>>
```

<!-- Ending the tabset section -->
<!-- ### {.toc-ignore} -->




# Scatterplot genes comparison {.tabset .tabset-fade}

```{r rmd_heterogeneity_scatter_genes, fig.dim = c(10, 10)}
parentLevel=1
<<scatter_genes>>
rm("parentLevel");
```

<!-- Ending the tabset section -->
# {.toc-ignore}
<br /><br />

```{r rmd_final_saveSessionImage}
<<final_saveSessionImage>>
```






