

# Marker genes
```{r rmd_heterogeneity_markerGenes}
<<heterogeneity_markerGenes>>
```

## Marker genes list
```{r rmd_heterogeneity_markerGenes_table}
<<heterogeneity_markerGenes_table>>
```
<br />

## Marker genes expression {.tabset .tabset-fade}

### UMAP {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_expression_projection_UMAP, fig.dim = c(4, 4), out.width='25%'}

cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_markerGenes_expression_projection>>

```

<!-- Ending the tabset section -->
<!-- ### {.toc-ignore} -->

<!-- ### tSNE {.tabset .tabset-fade} -->
<!-- ```{r rmd_heterogeneity_markerGenes_expression_projection_tSNE, fig.dim = c(4, 4), out.width='25%'} -->

<!-- cat("\n<a href='#clusters-projection'>"); -->
<!-- <<plotDimReducRaster_thumbnail>> -->
<!-- cat("</a> \n \n"); -->

<!-- <<heterogeneity_markerGenes_expression_projection>> -->

<!-- ``` -->

<!-- <!-- Ending the tabset section --> -->
<!-- #### {.toc-ignore} -->

### Clusters violin {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_expression_violin, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_markerGenes_expression_violin>>
```


### Clusters functional enrichment {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_functional_enrichment, fig.dim = c(9, 9) }
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

cat("Disabled in Rmd")
#<<heterogeneity_markerGenes_functional_enrichment>>
```


### Heatmap (mean) {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_heatmap_mean, fig.dim = c(9, 9) }
<<heterogeneity_markerGenes_heatmap_prepare>>
<<heterogeneity_markerGenes_heatmap_mean>>
```


### Heatmap (dot) {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_heatmap_dotplot, fig.dim = c(9, 9) }
<<heterogeneity_markerGenes_heatmap_dotplot>>
```


### Heatmap (full) {.tabset .tabset-fade}
```{r rmd_heterogeneity_markerGenes_heatmap_full, fig.dim = c(9, 9) }
<<heterogeneity_markerGenes_heatmap_full>>
```

<br /><br />





# Monitored genes
```{r rmd_heterogeneity_monitoredGenes, warning = TRUE}
<<heterogeneity_monitoredGenes>>
```

## Monitored genes heatmap

Expression heatmap of monitored genes sorted by Seurat clusters:

```{r rmd_heterogeneity_monitoredGenes_heatmap, fig.dim = c(8, min(1+(length(unlist(MONITORED_GENES))/10), 150))}
#<<heterogeneity_monitoredGenes_heatmap>>
```

## Monitored genes expression {.tabset .tabset-fade}

### UMAP {.tabset .tabset-fade}
```{r rmd_heterogeneity_monitoredGenes_expression_projection_UMAP, fig.dim = c(4, 4), out.width='25%'}

cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_monitoredGenes_expression_projection>>

```

<!-- Ending the tabset section -->
<!-- #### {.toc-ignore} -->

<!-- #### tSNE {.tabset .tabset-fade} -->
<!-- ```{r rmd_heterogeneity_monitoredGenes_expression_projection_tSNE, fig.dim = c(4, 4), out.width='25%'} -->

<!-- cat("\n<a href='#clusters-projection'>"); -->
<!-- #<<plotDimReducRaster_thumbnail>> -->
<!-- cat("</a> \n \n"); -->

<!-- #<<heterogeneity_monitoredGenes_expression_projection>> -->

<!-- ``` -->

<!-- <!-- Ending the tabset section --> -->
<!-- #### {.toc-ignore} -->

### Clusters violin {.tabset .tabset-fade}
```{r rmd_heterogeneity_monitoredGenes_expression_violin, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_monitoredGenes_expression_violin>>
```

<!-- Ending the tabset section -->
<!-- #### {.toc-ignore} -->

<!-- Ending the tabset section -->
<!-- ### {.toc-ignore} -->
<br /><br />




# Modules analysis
```{r rmd_heterogeneity_modules}
<<heterogeneity_modules>>
<<heterogeneity_modules_scoring>>
```

## Modules scoring heatmap

Heatmap of modules scoring sorted by Seurat clusters:

```{r rmd_heterogeneity_modules_heatmap, fig.dim = c(8, min(1+(length(MODULES_GENES)/10), 150))}
<<heterogeneity_modules_heatmap>>
```

## Modules scoring {.tabset .tabset-fade}

### UMAP {.tabset .tabset-fade .tabset-pills}
```{r rmd_heterogeneity_modules_expression_projection_UMAP, fig.dim = c(4, 4), out.width='25%'}

cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_modules_expression_projection>>
#<<heterogeneity_modules_expression_projection_pngFile>>

```

<!-- Ending the tabset section -->
### {.toc-ignore}

### Clusters violin {.tabset .tabset-fade}
```{r rmd_heterogeneity_modules_expression_violin, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
<<plotDimReducRaster_thumbnail>>
cat("</a> \n \n");

<<heterogeneity_modules_expression_violin>>
#<<heterogeneity_modules_expression_violin_pngFile>>
```

<!-- Ending the tabset section -->
<!-- ### {.toc-ignore} -->




# Scatterplot genes comparison {.tabset .tabset-fade}

```{r rmd_heterogeneity_scatter_genes, fig.dim = c(10, 10)}
parentLevel=1
<<scatter_genes>>
rm("parentLevel");
```
