---
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 3
---




<!-- Javascript for zooming on figures (adapted from: https://stackoverflow.com/questions/40401680) -->

<!-- Jquery import conflicts with DT::datatable so needs to be commented here -->
<!-- <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script> -->

<style>
.zoomDiv {
  display: none;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  background-color: #FFFFFF;
  box-shadow: 0px 0px 50px #888888;
  width: fit-content;
  max-width: 90%;
  max-height: 90%;
  overflow: auto;
}

.zoomImg {
  width: 100%;
}

.FixedHeightContainer
{
  height:500px;
  width:250px; 
  padding:5px; 
  background:#DDD;
}

.LargerFixedHeightContainer
{
  height:500px;
  width:500px; 
  padding:5px; 
  background:#DDD;
}


.MaxWidthFixedHeightContainer
{
  height:500px;
  width:100%; 
  padding:5px; 
  background:#DDD;
}

.Content
{
  height:450px;
  width:100%;
  overflow:auto;
  background:#fff;
}

</style>

<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick for all img except the zoomed one and link ones (filter)
    // use 'img.zoom' and out.extra='class=\"zoom\"' in chunk to specify manually which chunk images can be zoomed
    $('img:not(.zoomImg)').filter(':not(a *)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').show();
    });
    // onClick function for hiding div
    $('img.zoomImg').click(function() {
      $('.zoomDiv').hide();
    });
  });
</script>




```{r rmd_setKnitrOptions, include=FALSE}
# Set hook for PNG optimization ('optipng' must be installed on system)
#knitr::knit_hooks$set(optipng = knitr::hook_optipng)

# Set chunks default options
knitr::opts_chunk$set(results='asis',
                      echo = FALSE,           # Do not show chunks code
                      message = FALSE,        # Hide R regular text output in reports
                      warning = TRUE,         # Show warning messages
                      error = FALSE,          # Stop generating report on errors
                      cache = FALSE,          # Disable chunk result caching
                      cache.comments = FALSE, # Changing comments does not invalidate cache
#                      dev = "svg",            # Generate all figures as vectorized 'svg' files                      
                      fig.dim = c(5, 5),      # Size of device for R figures
                      autodep = TRUE,         # Automatic chunk dependencies if cache enabled
                      optipng = '-o2');       # PNG optimization level (2=default, 5=slow, 7=very slow)

knitr::knit_engines$set(python = reticulate::eng_python)
```




```{r rmd_loadParamsAndDependencies, warning=FALSE, cache = FALSE}
### Define working folder
WORKING_DIR   = getwd();


### Load libraries, global functions/variables, and chunks
source( file.path( WORKING_DIR, "00_generalDeps.R"));

# Import chunks from source files
read_chunk( path=file.path( WORKING_DIR, "01_prepareData.R"));
```




---
title: `r paste( GLOBAL_DESCRIPTION, ANALYSIS_STEP_NAME, sep ="<BR>")`
---




```{r rmd_initFunctions}

### Create output directory
dir.create( PATH_ANALYSIS_OUTPUT, showWarnings = FALSE);


### Record starting time (for report and file names)
startTime = Sys.time();
startTimeReport   = format( startTime, "%Y %m %d %H:%M:%S")
startTimeFileName = format( startTime, "%Y_%m_%d_%H_%M_%S")


### Initialize utils

# Create a hash for all parameters
paramsHash = digest( environment(), algo="murmur32");

# Create a 'safe' unique prefix for output files (now specified at project scale in globalParams.R)
#outputFilesPrefix = path_sanitize( gsub("([[:punct:]])|\\s+",
#                                        "_",
#                                        paste0(PROJECT_NAME, "_",
#                                               SAMPLE_NAME, "_",
#                                               startTimeFileName, "_",
#                                               paramsHash, "_")),
#                                   replacement = "_");

# Set seed for pseudo random number generator
set.seed(SEED);


# Set the use of multiple cores using 'future' library, as implemented in Seurat3 when possible
# https://github.com/satijalab/seurat/issues/457
plan(strategy = "multicore", workers = NBCORES);

# Create a hidden empty heatmap to prevent heatmapr interference with plotly functions (bug ?)
cat('<div style="display: none">');
main_heatmap(matrix(0));
cat('</div>');

# Create a hidden plotly in a tagList to allow using them in loops later
cat('<div style="display: none">');
htmltools::tagList(plot_ly(x = rnorm(10), type = "histogram"))
cat('</div>');

# Create a hidden empty datatable with same options as real ones to prevent a bug when showing them in loops later (columns filters not working)
cat('<div style="display: none">');
htmltools::tagList( datatable( data.frame("empty1" = 1:10, "empty2" = 1:10),
                               class = "compact",
                               filter="top",
                               rownames = FALSE,
                               extensions = c('Buttons', 'Select')))
cat('</div>');
```




## Run informations {.tabset .tabset-fade}

### Run
<center>
```{r rmd_runInfo_run}
pander( c( 'Date'     = startTimeReport,
           'Sample'   = EXPERIMENT_PROJECT_NAME,
           'Hash'     = paramsHash));
```
</center>

### Parameters
```{r rmd_runInfo_params}
listParams = as.list( environment());
pander(listParams[order(names(listParams))]); # Show params in alphabetical order
```

### System
<center>
```{r rmd_runInfo_sysInfo}
showSimpleDT( Sys.info())
```
</center>

### R
```{r rmd_runInfo_r}
pander( sessionInfo());
```

### Python
```{r rmd_reticulate}
# Do not load reticulate earlier, it prevents pander to render 'py' in 'Parameters'
library(reticulate);
```

```{python rmd_runInfo_python}
import sys
print("**Python version "+sys.version+"**")
print("\n\n")

import pkg_resources
print("**Libraries: **")
for i in [str(d).replace(" ","==") for d in pkg_resources.working_set]:
  print(i)
```


<!-- Ending the tabset section -->
## {.toc-ignore}
<br /><br />




## Load data (R/Seurat)
```{r rmd_loadData}
<<loadData>>
```
<br /><br />


