---
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 3
---




<!-- Javascript for zooming on figures (adapted from: https://stackoverflow.com/questions/40401680) -->

<!-- Jquery import conflicts with DT::datatable so needs to be commented here -->
<!-- <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script> -->

<style>
.zoomDiv {
  display: none;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  background-color: #FFFFFF;
  box-shadow: 0px 0px 50px #888888;
  width: fit-content;
  max-width: 90%;
  max-height: 90%;
  overflow: auto;
}

.zoomImg {
  width: 100%;
}
</style>

<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick for all img except the zoomed one and link ones (filter)
    // use 'img.zoom' and out.extra='class=\"zoom\"' in chunk to specify manually which chunk images can be zoomed
    $('img:not(.zoomImg)').filter(':not(a *)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').show();
    });
    // onClick function for hiding div
    $('img.zoomImg').click(function() {
      $('.zoomDiv').hide();
    });
  });
</script>




```{r rmd_setKnitrOptions, include=FALSE}
# Set hook for PNG optimization ('optipng' must be installed on system)
#knitr::knit_hooks$set(optipng = knitr::hook_optipng)

# Set chunks default options
knitr::opts_chunk$set(results='asis',
                      echo = FALSE,           # Do not show chunks code
                      message = FALSE,        # Hide R regular text output in reports
                      warning = FALSE,        # Show warning messages
                      error = FALSE,          # Stop generating report on errors
                      cache = FALSE,          # Disable chunk result caching
                      cache.comments = FALSE, # Changing comments does not invalidate cache
                      fig.dim = c(5, 5),      # Size of device for R figures
                      autodep = TRUE,         # Automatic chunk dependencies if cache enabled
                      optipng = '-o2',        # PNG optimization level (2=default, 5=slow, 7=very slow)
                      dev = 'svg');           # Set default rendering to SVG

# Set RMarkdown compatible format for kable 
options(knitr.table.format = 'markdown')
```




<!-- Load spectrum color picker code -->
```{js loadSpectrumJS, echo = FALSE, code=readLines("spectrum.js")}
```
```{css loadSpectrumCSS, echo = FALSE, code=readLines("spectrum.css")}
```

<!-- Prepare a js function extracting traces color from plotly figure -->
```{js getColorTab, echo = FALSE}

// Ask figure template from plotly, extract markers color (scatter and scattergl only), and place them in clipboard
getColorTab = function(plotLyFigure, type = "scatter", colorFormatFun = "hex") 
  { 
    var template = Plotly.makeTemplate(plotLyFigure);
    var resultColorString = "";
    for (curTrace in template.data[type])
    {
      // Only use traces having markers
      if(template.data[type][curTrace].mode == "markers") resultColorString += '"' + template.data[type][curTrace].name + '" = "' + tinycolor(template.data[type][curTrace].marker.color).toString(colorFormatFun) + '"\n';
    }
    // Create a dummy element to copy content to clipboard
    var textarea = document.createElement("textarea"); textarea.textContent = resultColorString; textarea.style.position = "fixed"; document.body.appendChild(textarea); textarea.select(); document.execCommand("copy"); document.body.removeChild(textarea);
    alert("\n" + resultColorString + "\n\nCopied to clipboard !");
  } 
```




```{r rmd_loadParamsAndDependencies, warning=FALSE, cache = FALSE}
### Define working folder
WORKING_DIR   = getwd();


### Load libraries, global functions/variables, and chunks
source( file.path( WORKING_DIR, "00_generalDeps.R"));

# Import chunks from source files
read_chunk( path=file.path( WORKING_DIR, "01_prepareData.R"));
#read_chunk( path=file.path( WORKING_DIR, "02_BCR.R"));
read_chunk( path=file.path( WORKING_DIR, "03_BCR_scRepertoire.R"));
read_chunk( path=file.path( WORKING_DIR, "90_finalize.R"));
```




---
title: `r paste( GLOBAL_DESCRIPTION, SAMPLE_NAME, ANALYSIS_STEP_NAME, sep ="<BR>")`
---




```{r rmd_initFunctions}

# Create output folders
<<createOutputFolders>>

### Record starting time (for report and file names)
startTime = Sys.time();
startTimeReport   = format( startTime, "%Y %m %d %H:%M:%S")
startTimeFileName = format( startTime, "%Y_%m_%d_%H_%M_%S")


### Initialize utils

# Create a hash for all parameters
paramsHash = digest( environment(), algo="crc32");

# Set seed for pseudo random number generator
set.seed(SEED);

# Set the use of multiple cores using 'future' library, as implemented in Seurat3 when possible
# https://github.com/satijalab/seurat/issues/457
plan(strategy = "multicore", workers = NBCORES);

```




# Run informations {.tabset .tabset-fade}

## Run
<center>
```{r rmd_runInfo_run}
pander( c( 'Date'     = startTimeReport,
           'Sample'   = EXPERIMENT_NAME,
           'Hash'     = paramsHash));
```
</center>

## Parameters
```{r rmd_runInfo_params}
listParams = as.list( paramsEnv);
pander(listParams[order(names(listParams))]); # Show params in alphabetical order
```

## System
<center>
```{r rmd_runInfo_sysInfo}
showSimpleDT( Sys.info())
```
</center>

## R
```{r rmd_runInfo_r}
pander( sessionInfo());
```

<!-- Ending the tabset section -->
<!-- ## {.toc-ignore} -->
<br /><br />


# Load single cell data

<br />
```{r rmd_dataLoad, warning = TRUE, fig.dim = c(9,6)}
<<loadData>>

<<screpertoire_load>>
```

<br /><br />

# Load contigs (scRepertoire)

```{r rmd_screpertoire_load, warning = TRUE, fig.dim = c(9,6)}
<<screpertoire_load>>
```

## Clonal abundance

```{r rmd_screpertoire_clonalAbundance, warning = TRUE, fig.dim = c(9,6)}
<<screpertoire_clonalAbundance>>
```

## Clonal length

```{r rmd_screpertoire_clonalLength, warning = TRUE, fig.dim = c(9,6)}
<<screpertoire_clonalLength>>
```

## Clonal homeostasis

```{r rmd_screpertoire_clonalHomeostasis, warning = TRUE, fig.dim = c(9,6)}
<<screpertoire_clonalHomeostasis>>
```

## Positional entropy

```{r rmd_screpertoire_positionalEntropy, warning = TRUE, fig.dim = c(9,6)}
<<screpertoire_positionalEntropy>>
```


# Combine GEX / Clonotypes

```{r rmd_screpertoire_combineGexBcr, warning = TRUE, fig.dim = c(9,6)}
<<screpertoire_combineGexBcr>>
```

## Clone size

```{r rmd_bcr_clone_size, warning = TRUE, fig.dim = c(9,6)}
<<bcr_clone_size>>
```





# BCR chains

## Descriptive statistics

```{r rmd_bcr_chains_stats, fig.dim = c(7,7)}
<<bcr_chains_stats>>
```

## Projection of chains {.tabset .tabset-fade}

```{r rmd_bcr_constant_chains_combination_projection, fig.dim = c(6,6), dev = 'png'}
<<bcr_constant_chains_combination_projection>>
```



# BCR clonotypes

## Descriptive statistics

```{r rmd_bcr_stats, fig.dim = c(7,7)}
<<bcr_clonotypes_stats>>
```


## Projection of top clonotypes (nbCells)

```{r rmd_bcr_top_clonotypes_projections, fig.dim = c(6,6), out.width = "25%", dev = 'png'}
<<bcr_top_clonotypes_projection>>
```

## Clonotypes counts {.tabset .tabset-fade}

### Top 50

```{r rmd_clonotype_counts_heatmap, fig.dim = c(17,11)}
# clonotype_colname = "clonotype_manual_heavy_and_light"
# Define an eventual subselection on object
#scObject = sc10x

<<clonotype_counts_heatmap>>
```




## Clonotypes overlap {.tabset .tabset-fade}

### Top 50 {.tabset .tabset-fade}

```{r rmd_clonotype_overlap_currentmouse, fig.dim = c(12, 10)}
#clonotype_colname = "clonotype_manual_heavy_and_light"
<<clonotype_overlap_currentmouse>>
```

### Custom: Top 50 {.tabset .tabset-fade}

```{r rmd_clonotype_overlap_customSergio, fig.dim = c(12,10)}
#clonotype_colname = "clonotype_manual_heavy_and_light"
<<clonotype_overlap_customSergio>>
```


## Circlize {.tabset .tabset-fade}

This function will take the meta data from the product of combineExpression() and generate a relational data frame to be used for a chord diagram. Each cord will represent the number of clone unique and shared across the multiple group.by variable. If using the downstream circlize R package, please read and cite the following manuscript.

### All: LN+LG

```{r rmd_bcr_clonotypes_circlize_ALL, fig.dim = c(10,10)}
<<bcr_clonotypes_circlize_ALL>>
```

### LN

```{r rmd_bcr_clonotypes_circlize_LN, fig.dim = c(10,10)}
<<bcr_clonotypes_circlize_LN>>
```

### LG

```{r rmd_bcr_clonotypes_circlize_LG, fig.dim = c(10,10)}
<<bcr_clonotypes_circlize_LG>>
```


## ClonalNetwork

This function generates a network based on clonal proportions of an indicated identity and then superimposes the network onto a single-cell object dimensional reduction plot.

```{r rmd_bcr_clonotypes_clonalNetwork_LN_LG, fig.dim = c(12,10), out.width = "50%"}
<<bcr_clonotypes_clonalNetwork_LN_LG>>
```


## Clonal bias

The metric seeks to quantify how individual clones are skewed towards a specific cellular compartment or cluster. A clone bias of 1 - indicates that a clone is composed of cells from a single compartment or cluster, while a clone bias of 0 - matches the background subtype distribution. Please read and cite the following manuscript if using clonalBias().

```{r rmd_bcr_clonotypes_clonalBias, fig.dim = c(12,10)}
<<bcr_clonotypes_clonalBias>>
```

## Venn

```{r rmd_bcr_clonotypes_venn, fig.dim = c(12,10)}
<<bcr_clonotypes_venn>>
```


## Venn Merge

This script relies on what 'venn' precomputed results (csv) it finds in output folder.
In a clean/new run without any precomputed csv file, the first report should only contain one bar, the second two, etc...
The "launch report compilation" script can be run twice to get a consistent plot in all reports (ther is a loop on mice/samples in this script to generate a report for each sample).
```{r rmd_bcr_clonotypes_venn_merge, fig.dim = c(4,4)}
<<bcr_clonotypes_venn_merge>>
```



<!-- Ending the tabset section -->
# {.toc-ignore}
<br /><br />





