---
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 3
---



<!-- Javascript for zooming on figures (adapted from: https://stackoverflow.com/questions/40401680) -->

<!-- Jquery import conflicts with DT::datatable so needs to be commented here -->
<!-- <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script> -->

<style>
.zoomDiv {
  display: none;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  background-color: #FFFFFF;
  box-shadow: 0px 0px 50px #888888;
  width: fit-content;
  max-width: 90%;
  max-height: 90%;
  overflow: auto;
}

.zoomImg {
  width: 100%;
}
</style>

<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick for all img except the zoomed one and link ones (filter)
    // use 'img.zoom' and out.extra='class=\"zoom\"' in chunk to specify manually which chunk images can be zoomed
    $('img:not(.zoomImg)').filter(':not(a *)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').show();
    });
    // onClick function for hiding div
    $('img.zoomImg').click(function() {
      $('.zoomDiv').hide();
    });
  });
</script>




```{r rmd_setKnitrOptions, include=FALSE}
# Set hook for PNG optimization ('optipng' must be installed on system)
#knitr::knit_hooks$set(optipng = knitr::hook_optipng)

# Set chunks default options
knitr::opts_chunk$set(results='asis',
                      echo = FALSE,           # Do not show chunks code
                      message = FALSE,        # Hide R regular text output in reports
                      warning = FALSE,        # Show warning messages
                      error = FALSE,          # Stop generating report on errors
                      cache = FALSE,          # Disable chunk result caching
                      cache.comments = FALSE, # Changing comments does not invalidate cache
                      fig.dim = c(5, 5),      # Size of device for R figures
                      autodep = TRUE,         # Automatic chunk dependencies if cache enabled
                      optipng = '-o2',        # PNG optimization level (2=default, 5=slow, 7=very slow)
                      dev = 'svg');           # Set default rendering to SVG

# Set RMarkdown compatible format for kable 
options(knitr.table.format = 'markdown')
```




<!-- Load spectrum color picker code -->
```{js loadSpectrumJS, echo = FALSE, code=readLines("spectrum.js")}
```
```{css loadSpectrumCSS, echo = FALSE, code=readLines("spectrum.css")}
```

<!-- Prepare a js function extracting traces color from plotly figure -->
```{js getColorTab, echo = FALSE}

// Ask figure template from plotly, extract markers color (scatter and scattergl only), and place them in clipboard
getColorTab = function(plotLyFigure, type = "scatter", colorFormatFun = "hex") 
  { 
    var template = Plotly.makeTemplate(plotLyFigure);
    var resultColorString = "";
    for (curTrace in template.data[type])
    {
      // Only use traces having markers
      if(template.data[type][curTrace].mode == "markers") resultColorString += '"' + template.data[type][curTrace].name + '" = "' + tinycolor(template.data[type][curTrace].marker.color).toString(colorFormatFun) + '"\n';
    }
    // Create a dummy element to copy content to clipboard
    var textarea = document.createElement("textarea"); textarea.textContent = resultColorString; textarea.style.position = "fixed"; document.body.appendChild(textarea); textarea.select(); document.execCommand("copy"); document.body.removeChild(textarea);
    alert("\n" + resultColorString + "\n\nCopied to clipboard !");
  } 
```




```{r rmd_loadParamsAndDependencies, warning=FALSE, cache = FALSE}
### Define working folder
WORKING_DIR   = getwd();


### Load libraries, global functions/variables, and chunks
source( file.path( WORKING_DIR, "00_generalDeps.R"));

# Import chunks from source files
read_chunk( path=file.path( WORKING_DIR, "01_prepareData.R"));
read_chunk( path=file.path( WORKING_DIR, "08_IghE_expressing_cells.R"));
read_chunk( path=file.path( WORKING_DIR, "09_IghE_expressing_VS_others.R"));
read_chunk( path=file.path( WORKING_DIR, "90_finalize.R"));
```




---
title: `r paste( GLOBAL_DESCRIPTION, SAMPLE_NAME, ANALYSIS_STEP_NAME, sep ="<BR>")`
---




```{r rmd_initFunctions}

# Create output folders
<<createOutputFolders>>

### Record starting time (for report and file names)
startTime = Sys.time();
startTimeReport   = format( startTime, "%Y %m %d %H:%M:%S")
startTimeFileName = format( startTime, "%Y_%m_%d_%H_%M_%S")


### Initialize utils

# Create a hash for all parameters
paramsHash = digest( environment(), algo="crc32");

# Set seed for pseudo random number generator
set.seed(SEED);

# Set the use of multiple cores using 'future' library, as implemented in Seurat3 when possible
# https://github.com/satijalab/seurat/issues/457
plan(strategy = "multicore", workers = NBCORES);

```




# Run informations {.tabset .tabset-fade}

## Run
<center>
```{r rmd_runInfo_run}
pander( c( 'Date'     = startTimeReport,
           'Sample'   = EXPERIMENT_NAME,
           'Hash'     = paramsHash));
```
</center>

## Parameters
```{r rmd_runInfo_params}
listParams = as.list( paramsEnv);
pander(listParams[order(names(listParams))]); # Show params in alphabetical order
```

## System
<center>
```{r rmd_runInfo_sysInfo}
showSimpleDT( Sys.info())
```
</center>

## R
```{r rmd_runInfo_r}
pander( sessionInfo());
```

<!-- Ending the tabset section -->
<!-- ## {.toc-ignore} -->
<br /><br />


# Load single cell data

<br />
```{r rmd_dataLoad, warning = TRUE, fig.dim = c(9,6)}
<<loadData>>
```

<br /><br />




# IgE Expression {.tabset .tabset-fade .tabset-pills}

```{r rmd_plot_umap_ige_positive_cells_prepare_data}
<<plotsPreparation>>
<<plot_umap_ige_positive_cells_prepare_data>>
```

## Positive cells
```{r rmd_plot_umap_ige_positive_cells, fig.dim = c( 10, 10)}
<<plot_umap_ige_positive_cells>>
```

## Split tissue
```{r rmd_plot_umap_ige_positive_cells_split_tissue, fig.dim = c( 16, 8)}
<<plot_umap_ige_positive_cells_split_tissue>>
```

## Color tissue
```{r rmd_plot_umap_ige_positive_cells_color_by_tissue, fig.dim = c( 10, 10)}
<<plot_umap_ige_positive_cells_color_by_tissue>>
```

## Color cluster
```{r rmd_plot_umap_ige_positive_cells_split_mouse_color_by_cluster, fig.dim = c( 10, 10)}
<<plot_umap_ige_positive_cells_split_mouse_color_by_cluster>>
```



# Ige VS Ohers {.tabset .tabset-fade}

## LN

Cell identity based on highest igh expression (NA => None expressed)

```{r rmd_ige_vs_others_LN}
scObject = subset(sc10x, subset = HTOTISSUE_classification == "LN")
<<ige_vs_others>>
```


### Ige expression distribution {.tabset .tabset-fade .tabset-pills}

#### Global
```{r rmd_ige_expression_distribution_LN, fig.dim = c( 8, 7)}
<<ige_expression_distribution>>
```

#### Color: Cluster
```{r rmd_ige_expression_distribution_colorCluster_LN, fig.dim = c( 8, 7)}
<<ige_expression_distribution_colorCluster>>
```

#### Color: IgIdentity
```{r rmd_ige_expression_distribution_colorIgIdent_LN, fig.dim = c( 8, 7)}
<<ige_expression_distribution_colorIgIdent>>
```

#### Color: Cluster - Facet: IgIdentity
```{r rmd_ige_expression_distribution_colorCluster_facetIgIdent_LN, fig.dim = c( 10, 7)}
<<ige_expression_distribution_colorCluster_facetIgIdent>>
```



### Ige transcribing cells by identity and cluster

ighe-transcribing cells were associated with each cluster and constant region. Cells of the grid are labeled by the total number of ighe-transcribing cells and colored by the percentage of cells in each cluster that are IGHE-transcribing.

```{r rmd_ige_vs_others_table_LN, fig.dim = c( 7, 7)}
<<ige_vs_others_table>>
```





## LG

Cell identity based on highest igh expression (NA => None expressed)

```{r rmd_ige_vs_others_LG}
scObject = subset(sc10x, subset = HTOTISSUE_classification == "LG")
<<ige_vs_others>>
```


### Ige expression distribution {.tabset .tabset-fade .tabset-pills}

#### Global
```{r rmd_ige_expression_distribution_LG, fig.dim = c( 8, 7)}
<<ige_expression_distribution>>
```

#### Color: Cluster
```{r rmd_ige_expression_distribution_colorCluster_LG, fig.dim = c( 8, 7)}
<<ige_expression_distribution_colorCluster>>
```

#### Color: IgIdentity
```{r rmd_ige_expression_distribution_colorIgIdent_LG, fig.dim = c( 8, 7)}
<<ige_expression_distribution_colorIgIdent>>
```

#### Color: Cluster - Facet: IgIdentity
```{r rmd_ige_expression_distribution_colorCluster_facetIgIdent_LG, fig.dim = c( 10, 7)}
<<ige_expression_distribution_colorCluster_facetIgIdent>>
```



### Ige transcribing cells by identity and cluster

ighe-transcribing cells were associated with each cluster and constant region. Cells of the grid are labeled by the total number of ighe-transcribing cells and colored by the percentage of cells in each cluster that are IGHE-transcribing.

```{r rmd_ige_vs_others_table_LG, fig.dim = c( 7, 7)}
<<ige_vs_others_table>>
```






## ALL

Cell identity based on highest igh expression (NA => None expressed)

```{r rmd_ige_vs_others_ALL}
scObject = sc10x
<<ige_vs_others>>
```


### Ige expression distribution {.tabset .tabset-fade .tabset-pills}

#### Global
```{r rmd_ige_expression_distribution_ALL, fig.dim = c( 8, 7)}
<<ige_expression_distribution>>
```

#### Color: Cluster
```{r rmd_ige_expression_distribution_colorCluster_ALL, fig.dim = c( 8, 7)}
<<ige_expression_distribution_colorCluster>>
```

#### Color: IgIdentity
```{r rmd_ige_expression_distribution_colorIgIdent_ALL, fig.dim = c( 8, 7)}
<<ige_expression_distribution_colorIgIdent>>
```

#### Color: Cluster - Facet: IgIdentity
```{r rmd_ige_expression_distribution_colorCluster_facetIgIdent_ALL, fig.dim = c( 10, 7)}
<<ige_expression_distribution_colorCluster_facetIgIdent>>
```



### Ige transcribing cells by identity and cluster

ighe-transcribing cells were associated with each cluster and constant region. Cells of the grid are labeled by the total number of ighe-transcribing cells and colored by the percentage of cells in each cluster that are IGHE-transcribing.

```{r rmd_ige_vs_others_table_ALL, fig.dim = c( 7, 7)}
<<ige_vs_others_table>>
```


